---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(ggplot2)
library(rtist)
```

# rtist

[![Travis build status](https://travis-ci.org/tomasokal/rtist.svg?branch=master)](https://travis-ci.org/tomasokal/rtist)
[![status](https://tinyverse.netlify.com/badge/<package>)](https://CRAN.R-project.org/package=rtist)

## Overview

"They'll sell you thousands of greens. Veronese green and emerald green and cadmium green and any sort of green you like; but that particular green, never." - *Pablo Picasso, (1966)*

Use the palettes of famous artists in your own visualizations. 

## Installation

Install the latest version from GitHub.

``` {r, eval = FALSE}
# Install remotes to download.
install.packages("remotes")

# And then install from github.
remotes::install_github("tomasokal/rtist")
```

## Palettes

`rtist` provides color palettes from famous artists and paintings. You can quickly view and see all possible palettes using `rtist_help()`.

``` {r help}
# Load package
library(rtist)

# Display possible palettes
rtist::rtist_help()
```

There are 15 palettes total.

``` {r palette, fig.height = 5, echo = FALSE}
library(rtist)
par(mfrow=c(5,3))
for(i in names(rtist_palettes)) print(rtist_palette(i))
```

After finding a palette, go ahead and select that palette along with however many colors you want.

``` {r palettes, eval = FALSE}
# Load package
library(rtist)

# Choose Warhol
rtist::rtist_palette("warhol")

# Choose 4 colors from Picasso
rtist::rtist_palette("picasso", 4)
```

```{r ggplot, echo = FALSE}
library(ggplot2)
library(rtist)

pal <- rtist::rtist_palette("hopper")

ggplot2::ggplot(iris, aes(Sepal.Length, Sepal.Width, color = Species)) +
    geom_jitter(size = 3) +
    theme_minimal() +
    scale_color_manual(values = pal)
```

## Credits

This package was mostly built to teach me package development. It was largely inspired by [Ewen Henderson’s `ghibli`
package](https://github.com/ewenme/ghibli) and [Karthik Ram’s `wesanderson` 
package](https://github.com/karthik/wesanderson).

The palettes themselves come from [10 Color Palettes Based on Famous Paintings](http://www.skellermeyerdesigns.com/blog/10-color-palettes-based-on-famous-paintings) and [Color Lisa](http://colorlisa.com/). Check those out for other awesome palettes.




